---
title: "p8105_HW1_mh4589"
output: github_document
date: "2024-09-14"
---
```{r libraryverse, message=FALSE}
library (tidyverse)
```

## Problem 1

Load the penguins dataset.
```{r penquins}
data("penguins", package = "palmerpenguins")

```

#### Description of the dataset
Here are the variables of the penguins dataset:

**Species**: The species of the penguin (Adelie, Chinstrap, or Gentoo).

**Island**: The island where the penguin was observed (Biscoe, Dream, or Torgersen).

**Bill_length_mm**: The length of the penguin's bill in millimeters.

**Bill_depth_mm**: The depth of the penguin's bill in millimeters.

**Flipper_length_mm**: The length of the penguin's flipper in millimeters.

**Body_mass_g**: The body mass of the penguin in grams.

**Sex**: The sex of the penguin (male or female)

The data set has `r ncol(penguins)` columns and `r nrow(penguins)` rows.

The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` milimeters.

```{r penguin_plot, echo = FALSE}
#make a scatterplot with flipper length on x-axis and bill on y-axis. use color = species to categorize by species.
ggplot(penguins,aes (x=flipper_length_mm, y=bill_length_mm, color = species)) +
  geom_point()


ggsave("hw1_penguinsplot.pdf")

```

## Problem 2
```{r rnorm_df}
#create a 10x4 data frame. Length is 10. 4 different vectors 
rnorm_df = 
  tibble (
    norm_samp = rnorm(10),
    vec_logical = norm_samp > 0,
    vec_character = c("Item 1", "Item 2", "Item 3", "Item 4", "Item 5", "Item 6", "Item 7", "Item 8", "Item 9", "Item 10"),
    vec_factor = factor(sample(c("level 1", "level 2", "level 3"), 10, replace = TRUE)))
  
print(rnorm_df)

```
