---
title: "p8105_HW1_mh4589"
author: "My An Huynh"
output: github_document
date: "2024-09-21"
---
```{r library, message = FALSE}
library (tidyverse)
```

## Problem 1

Load the penguins dataset.
```{r penquins}
data("penguins", package = "palmerpenguins")

```

#### Description of the dataset
The penguins dataset contains information on three different penguin species (Adelie, Chinstrap and Gentoo). Here are the important variables of the penguins dataset:

**Species**: The species of the penguin (Adelie, Chinstrap, or Gentoo).

**Island**: The island where the penguin was observed (Biscoe, Dream, or Torgersen).

**Bill_length_mm**: The length of the penguin's bill in millimeters.

**Bill_depth_mm**: The depth of the penguin's bill in millimeters.

**Flipper_length_mm**: The length of the penguin's flipper in millimeters.

**Body_mass_g**: The body mass of the penguin in grams.

**Sex**: The sex of the penguin (male or female)

The data set has `r ncol(penguins)` columns and `r nrow(penguins)` rows.

The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` milimeters.

The scatterplot was constructed with bill length on x-axis and flipper length on y-axis. I used color = species to categorize by species.

```{r penguin_plot}


ggplot(penguins,aes (
  x=bill_length_mm, 
  y=flipper_length_mm,
  color = species)) +
  geom_point() +
  labs(title = "Bill Length vs Flipper Length for 3 Penguin Spcies",
       x = "Bill Length (mm)",
       y = "Flipper Length (mm)")


ggsave("hw1_penguinsplot.pdf")

```

## Problem 2
Created a dataframe named rnorm_df with 4 different vectors - norm_samp, logical, character and factor.

```{r rnorm_df}
#create a 10x4 data frame. Length is 10. 4 different vectors 
rnorm_df = 
  tibble (
    norm_samp = rnorm(10),
    vec_logical = norm_samp > 0,
    vec_character = c("a","b","c","d","e","f","g","h","i","j"),
    vec_factor = factor(c("level 1", "level 2", "level 3","level 1", "level 2", "level 3", "level 1","level 1", "level 2", "level 3"))
)
```

I used the pull function to calculate the mean. The mean function only works for norm_samp because it is a numeric column, and for vec_logical because TRUE is assigned a value of 1 and FALSE is assigned a value of 0. The mean function does not work on the character and factor vectors. 

```{r mean_rnorm}

mean_norm_samp =  mean(pull(rnorm_df, norm_samp))
mean_norm_samp

mean_vec_character = mean(pull(rnorm_df, vec_character), na.rm = TRUE)
mean_vec_character

mean_vec_logical = mean(pull(rnorm_df, vec_logical))
mean_vec_logical

mean_vec_factor = mean(pull(rnorm_df, vec_factor))
mean_vec_factor
```

When I applied the as.numeric function, I was able to calculate the mean for the logical and factor vectors, but not the character vector. This is because the as.numeric function assigns value 1 for TRUE and 0 for FALSE to the logical vector, and it assigns values 1,2,3 for the 3 different levels in the factor vector, but it cannot assign numeric values to characters in the character vector. 
```{r num_rnorm,  echo = FALSE}
num_vec_character = as.numeric(pull(rnorm_df, vec_character))
num_vec_logical = as.numeric(pull(rnorm_df, vec_logical))
num_vec_factor = as.numeric(pull(rnorm_df, vec_factor))

```

```{r mean_num_rnorm, echo = FALSE}
mean_num_char = mean(num_vec_character)
mean_num_char

mean_num_logical = mean(num_vec_logical)
mean_num_logical

mean_num_factor = mean(num_vec_factor)
mean_num_factor
```

